Rjags parameters

### 2020-09-12 Scripts/Rjags.tunning.Rmd
without site

---
title: "Rjags parameters"
output: html_notebook
---
Adjusting rjags parameters to see how they affect the prob of presence of a particular ASV in the dataset

@@

>>>>

---
title: "Rjags parameters"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
Adjusting rjags parameters to see how they affect the prob of presence of a particular ASV in the dataset

@@

## Without Site into the mix
```{r}
ASV.nested %>% 
    ungroup() %>% 
  select(Step2.tibble) %>% 
  unnest(Step2.tibble) %>%

  separate(sample, into = c("biol","rep"), sep = "\\.") %>%
  mutate(nReads = 1) %>% 
  spread(key = "rep", value = "nReads", fill= 0,drop = F) %>% 
  group_by(Hash) %>%
  mutate(ndetections = `1`+`2`+`3`) %>% 
   group_by(ndetections, Hash) %>%
  summarise(tot = sum(!is.na(ndetections))) %>% 
  spread(ndetections, tot,fill = 0) %>% 
  unite(repetition.level,`1`,`2`,`3`, sep = ".") -> Pattern.of.presence2
```

```{r}
Pattern.of.presence2 %>% 
  group_by(repetition.level) %>% 
  select(-`0`) %>% 
  summarise(first = head(Hash, 1)) -> key.fromrep.to.hash
key.fromrep.to.hash %>% 
  pull(first) -> Hashes.to.run

```{r}
ASV.nested %>% 
    ungroup() %>% 
  select(Step2.tibble) %>% 
  unnest(Step2.tibble) %>%

  separate(sample, into = c("biol","rep"), sep = "\\.") %>%
  mutate(nReads = 1) %>% 
  spread(key = "rep", value = "nReads", fill= 0,drop = F) %>% 
  filter (Hash %in% Hashes.to.run) %>% 
  nest(-Hash) -> Nested.Hashes

for (i in 1:10){
  all.hashes <- model.round.nested(Nested.Hashes, n = i)
}
```
